---
title: "Intro to SFAplus package"
author: "Vaclav Hausenblas"
date: "2016-04-01"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
```{r Init}
require(SFAt)
# require(msm) # package for drawing from truncated-normal distribution
# require(data.table) # for more convenient data manipulation
```


## Basic SFA models

### Example dataset

Lets generate some randomly simulated production data,

```{r}
data_ex1 <- as.data.frame(sim_data_cs(1000, 
                                      x_coeff = c(50, 4, 2), 
                                      z_coeff = c(20), 
                                      sigma_u = 10, sigma_v = 5))

```

and explore the production data and simulated inefficiency term.

```{r}
# require(GGally)
# ggpairs(dtDT)

plot(data_ex1)
hist(data_ex1$y)
hist(data_ex1$u)
hist(data_ex1$eps)

```

## SFA -- normal/t-normal model

```{r}
model_ex1 <- sfa.fit(y = data_ex1$y,
                     X = cbind(a = data_ex1$x1, b = data_ex1$x2),
                     CM = NULL,   
                     dist = "tnorm",
                     opt_control = list(temp = 1, tmax = 20, maxit = 6e4)
                     # deb = T, debll = T
)

print(summary(model_ex1))
print(lrtest(model_ex1))
```


```{r}
ineff_fit <- inefficiencyTerm(model_ex1, estimator = "JLMS")
hist(ineff_fit)
```

Check for separation of frontier and actual production data
```{r}
yhat <- predict(model_ex1, type = "frontier")
hist(yhat,       xlim = c(0, max(data_ex1$y)))
hist(data_ex1$y, xlim = c(0, max(data_ex1$y)))
```

```{r}
hist(inefficiencyTerm(model_ex1, estimator = "JLMS"))
```

```{r}
hist(efficiency(model_ex1))
```

## SFA model with endogenous inefficiency mean 

### Generate random cross-section dataset
```{r}
data_ex2_cm <- as.data.frame(sim_data_cs(1000, 
                                         x_coeff = c(50, 4, 2), 
                                         z_coeff = c(20, -2, 2), 
                                         sigma_u = 10, sigma_v = 5))

```

### Fit BC95 model
```{r}

model_ex2 <- sfa.fit(y = data_ex2_cm$y,
                     X = cbind(a = data_ex2_cm$x1, b = data_ex2_cm$x2),
                     CM = cbind(c = data_ex2_cm$z1, d = data_ex2_cm$z2),
                     dist = "tnorm",
                     # deb = T, debll = T,
                     opt_method = "SANN",
                     opt_control = list(maxit = 50e3))

# print(model_ex2$coeff_frontier)
# print(model_ex2$coeff_cm)
# print(model_ex2$coeff_cv_u)
# print(model_ex2$coeff_cv_v)
print(summary(model_ex2))
print(lrtest(model_ex2))
```

### Fitted inefficiency term ($E(u_i|\epsilon_i)$)

```{r}
ex2_ineff_term <- predict(model_ex2, 
                          type = "inefficiency", 
                          estimator = "JLMS")

hist(ex2_ineff_term)
```

### Fitted efficiency (%)
```{r}
ex2_efficiencies <- predict(model_ex2, 
                            type = "efficiency", 
                            estimator = "JLMS")

hist(ex2_efficiencies)
```


```{r formula method}

sfa1 <- SFA(y ~ x1 + x2,
                 data = data_ex1,
                 dist = "hnorm",
                 form = "production",
                 # cm = ~ 0,  
                 # grad = "fd",
                 grad = "analytic",
                 opt_strategy = 1,
                 nlopt_opts = list("algorithm" = "NLOPT_LN_PRAXIS", print_level = 1, maxeval = 1e4, xtol_rel = 1e-10,
                                   "local_opts" = list("algorithm" = "NLOPT_LN_PRAXIS", print_level = 1, maxeval = 1e3, xtol_rel = 1e-10)),
                 nlopt_bounds = list(lb = -5, ub = 60),
                 optim_method = "BFGS",
                 optim_control = list(trace = 1, maxeval = 10000),
                 maxLik_method = "NR",
                 maxLik_control = list(printLevel = 3)
                 #,deb = T#, debll = T
)

print(summary(sfa1))
print(lrtest(sfa1))

```

