---
title: "Intro to SFAplus package"
author: "Vaclav Hausenblas"
date: "2016-04-01"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
  This document shows and test basic routines of SFAplus package.
  
  ```{r}
# require(SFAplus)
# require(msm) # package for drawing from truncated-normal distribution
# require(data.table) # for more convenient data manipulation
```


### Example dataset

Lets generate some randomly simulated production data,

```{r}
source("simulate_data.R")

data1 <- as.data.frame(sim_data(1000))

```

and explore the production data and simulated inefficiency term.

```{r}
# require(GGally)
# ggpairs(dtDT)

plot(data1)
hist(data1$y)
hist(data1$u)
hist(data1$eps)

```
## SFA -- normal/t-normal model

```{r}

sfa1 <- SFAplus::sfa.fit(y = data1$y,
                         X = cbind(a = data1$x1, b = data1$x2),
                         Z = NULL,    
                         dist = "exp",
                         spec  = NULL,
                         deb = T,
                         # control_opt = list(maxit = 300)
)

SFAplus:::summary.sfa(sfa1)
```


## SFA model with endogenous inefficiency mean 

```{r}

est <- SFAplus::sfa.fit(y = data1$y,
                        X = cbind(a = data1$x1, b = data1$x2),
                        Z = cbind(c = data1$z1, d = data1$z2),
                        spec  = "bc95",
                        deb = F,
                        # control_opt = list(maxit = 300)
)

SFAplus:::summary.sfa(est)
```


## OLS model

We might be interested in simple OLS model for LR test (and starting values of parameters).

```{r}

lmfit <- lm(y ~ x1 + x2 + I(-z1) + I(-z2), data = data1)
summary(lmfit)

```


